Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-07-25 doc/PRF2022/PRF_main.tex
fixed merge issues

The total force $\FF_i,$ and torque $T_i$ from the hydrodynamic
stress on each particle (with subscript `$i$') balance the force and
torque from the hydrophobic potential. 
%$\FF_i$ and $T_i$ are to be in balance with the force and torque from the hydrophobic interactions between the
%particles and the viscous solvent. 
As in~\citet{Fu2022_JFM} such a hydrophobic attraction potential
$u(\xx,t)$ is assumed to the minimizer of the free energy
\begin{align}
=======
velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.

Without inertia, $(\uu, p)$ also satisfy the force-free and torque-free conditions.
This means that the force and torque from the hydrodynamic stress on each particle 
are in balance with the total
force and torque coming from the hydrophobic potential and repulsion \cite{Fu2022_JFM}.
To compute this balance, we define
the free energy\cite{Fu2022_JFM}
\begin{equation}
>>>>>>> e6ff8abf65732bc50432a8d6cd9352c76cb936ca
\label{eq:free_energy}
F = \gamma
\int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2
\,d\xx
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right), \quad
\end{equation}
where $u(\xx,t)$ is as an order parameter for the structure of water,
$\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
$c$ is an ``effective" distance between particle centers, below which the steric repulsion between a pair of JPs becomes important.
In the followings we let $c$ be the radius of each JP.

The governing equation for $u(\xx,t)$ is obtained by computing the
domain variation of the free energy $F$~\cite{Fu20}. We obtain a
screened Laplace equation boundary value problem as a model for the
hydrophobic interaction between water and JPs:
\begin{alignat}{3}
  \label{eq:SLpde}
  -\rho^2 \Delta u + u &= 0,\qquad &&\xx \in \Omega, \\
  \label{eq:SLbc}
  u &= g, &&\xx \in \bd\Omega, \\
  \label{eq:SLfarfield}
  u &\rightarrow 0, &&|\xx| \rightarrow \infty,
\end{alignat}
where the boundary condition $g$ gives the degree of hydrophobicity the
=======
The parameter $\rho_0$ is an ``effective" distance between particle centers,
below which the steric repulsion between a pair of JPs becomes important.

The order parameter $u(\xx,t)$ is assumed to the minimizer of the free energy $F$ \cite{Fu20}.
Its governing equations $u(\xx,t)$ 
are a screened Laplace equation boundary value problem
as a model for the hydrophobic interaction between water and JPs:
\begin{gather}
  \label{eq:SL}
  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
  \label{eq:SLbc}
  u = g, \quad \xx \in \bd\Omega, \quad 
  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
\end{gather}
The boundary condition $g$ encodes hydrophobic properties of the
>>>>>>> e6ff8abf65732bc50432a8d6cd9352c76cb936ca
particle-solvent interface.

To get forces and torques from the free energy,
we compute the variation of the domain of the free energy 
\eqref{eq:free_energy} subject to \eqref{eq:SL}-\eqref{eq:SLbc},
and obtain 
\begin{equation}
  \FF_i \equiv \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
  - \frac{M}{\rho_0}
  \sum_{j \neq i}
  \frac{\aa_i - \aa_j}{|\aa_i - \aa_j|}
P'\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right)
  ,\quad
T_i \equiv \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
\end{equation}
for $i = 1,\dots,N_b$ with particle outward normal $\nu$. The term 
$
\mathbf{T}
= \gamma \left[ \rho^{-1} u^2 \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
$
is the hydrophobic stress.
Repulsion is rotationally symmetric and does not contribute to the torque.
The derivation details are found in \citet{Fu20}.

>>>>

The total force $\FF_i,$ and torque $T_i$ from the hydrodynamic
stress on each particle (with subscript `$i$') balance the force and
torque from the hydrophobic potential. 
%$\FF_i$ and $T_i$ are to be in balance with the force and torque from the hydrophobic interactions between the
%particles and the viscous solvent. 
As in~\citet{Fu2022_JFM} such a hydrophobic attraction potential
$u(\xx,t)$ is assumed to the minimizer of the free energy
\begin{equation}
\label{eq:free_energy}
F = \gamma
\int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2
\,d\xx
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right), \quad
\end{equation}
where $u(\xx,t)$ is as an order parameter for the structure of water,
$\rho$ is a decay length, and $\gamma$ is an interfacial tension.  The
radius of the Janus particles $c$ also serves as an ``effective"
distance between particle centers, below which the steric repulsion
between a pair of JPs becomes important.

The governing equation for $u(\xx,t)$ is obtained by computing the
domain variation of the free energy $F$~\cite{Fu20}. We obtain a
screened Laplace equation boundary value problem as a model for the
hydrophobic interaction between water and JPs:
\begin{alignat}{3}
  \label{eq:SLpde}
  -\rho^2 \Delta u + u &= 0,\qquad &&\xx \in \Omega, \\
  \label{eq:SLbc}
  u &= g, &&\xx \in \bd\Omega, \\
  \label{eq:SLfarfield}
  u &\rightarrow 0, &&|\xx| \rightarrow \infty,
\end{alignat}
The boundary condition $g$ encodes hydrophobic properties of the
particle-solvent interface. The parameter $\rho_0$ is an ``effective"
distance between particle centers, below which the steric repulsion
between a pair of JPs becomes important.
\todo[inline]{We are calling both $c$ and $\rho_0$ as this ``effective"
distance (see above). Also, $\rho_0$ is not defined. Should it be
$\rho$?}

To calculate forces and torques from the free energy, we compute the
variation of the domain of the free energy~\eqref{eq:free_energy}
subject to~\eqref{eq:SLpde}--\eqref{eq:SLbc}, and obtain 
\begin{equation}
  \FF_i \equiv \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
  - \frac{M}{\rho_0}
  \sum_{j \neq i}
  \frac{\aa_i - \aa_j}{|\aa_i - \aa_j|}
P'\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right)
  ,\quad
T_i \equiv \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
\end{equation}
for $i = 1,\dots,N_b$ with particle outward normal $\nu$. The term 
\begin{align}
\mathbf{T}
= \gamma \left[ \rho^{-1} u^2 \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
\end{align}
is the hydrophobic stress. Repulsion is rotationally symmetric and does
not contribute to the torque. The derivation details are found
in~\citet{Fu20}.
